Hot and fresh: Temperature, salinity, and seagrass change in a large Gulf coast estuary

### 2023-08-17 index.qmd
moved all figs and R files for eda to separate folder

```{r}
#| out-width: 70%
knitr::include_graphics(here('figs/sktall.png'))
```

@@

  chnk <- paste0('![](figs/', fls[mo], '){width=70%}\n')
  cat(chnk)

@@

  chnk <- paste0('![](figs/', fls[loc], ')\n')
  cat(chnk)

@@

```{r}
knitr::include_graphics(here('figs/tempgamex.png'))
knitr::include_graphics(here('figs/tempexceed.png'))
knitr::include_graphics(here('figs/tempcount.png'))
```

@@

```{r}
knitr::include_graphics(here('figs/saligamex.png'))
knitr::include_graphics(here('figs/saliexceed.png'))
knitr::include_graphics(here('figs/salicount.png'))
```

>>>>

```{r}
#| out-width: 70%
knitr::include_graphics(here('figseda/sktall.png'))
```

@@

  chnk <- paste0('![](figseda/', fls[mo], '){width=70%}\n')
  cat(chnk)

@@

  chnk <- paste0('![](figseda/', fls[loc], ')\n')
  cat(chnk)

@@

```{r}
knitr::include_graphics(here('figseda/tempgamex.png'))
knitr::include_graphics(here('figseda/tempexceed.png'))
knitr::include_graphics(here('figseda/tempcount.png'))
```

@@

```{r}
knitr::include_graphics(here('figseda/saligamex.png'))
knitr::include_graphics(here('figseda/saliexceed.png'))
knitr::include_graphics(here('figseda/salicount.png'))
```

### 2023-08-17 manu-draft.qmd
moved all figs and R files for eda to separate folder

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "Title"
bibliography: refs.bib
# csl: limnology-and-oceanography.csl
author: 
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true

>>>>

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "Hot and fresh: Temperature, salinity, and seagrass change in a large Gulf coast estuary"
bibliography: refs.bib
# csl: limnology-and-oceanography.csl
author: 
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
